Social Computing Article\thanks{This title is temporary}

### 2013-01-17 Article.tex
Adicionei referências, mudei pro estilo da ijcai e mais umas coisas

%\documentclass{article}
%\usepackage{ijcai13}
%\usepackage{times}
%\usepackage{latexsym}

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{algorithm2e}
\frenchspacing

@@

For years multi-agent systems have been used to research cooperation as a tool for problem-solving. Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents. Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems. However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour. In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment. The control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the ones displayed by humans.

@@

The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal.

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT) and the popular \emph{Sudoku} game, with individuals connected through the network being able to exchange partial solutions of the problem in question. There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:

@@

\section{System Overview}

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. We conceived a novel method for artificial social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.

@@

@@

\begin{figure}
\includegraphics[scale=0.47]{progression}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
}
\label{fig:progression}
\end{figure}

\section{Conclusions}

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. Thus, having in mind the fact that the strategies employed by human subjects are often not the most efficient, we proposed a collection of guidelines concerning the design of human computation systems, which intend to improve the performance of the human subjects they employ.

>>>>

\documentclass{article}
\usepackage{ijcai13}
\usepackage{times}
\usepackage{latexsym}

%\documentclass[letterpaper]{article}
%\usepackage{aaai}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
\usepackage{algorithm2e}
%\frenchspacing

@@

For years multi-agent systems have been used to research cooperation as a tool for problem-solving. Recently, however, there has been an increasing interest in the study of human beings as problem-solving agents. Several experiments have been conducted in which subjects are connected in a network with the goal of collectively solving a specific problem, and those have helped shed some light on the way humans interact to solve problems as well as on the dynamics of working groups~\cite{woolley:evidencecollective}. However, although those studies can provide us with observations and hypotheses, there is still a difficulty in finding ways to explain the observed behaviour. In this paper, we use a multi-agent based simulation to complement the study of human computation, as a way of explaining the strategies used by humans and understanding their consequences in a cooperative environment. The control that simulations provide us over the behaviour of the agents allows us to better understand possible reasons for the ones displayed by humans.

@@

The series of experiments summarized in~\cite{kearns:experim} are among the first to try to take advantage of the collective's problem-solving abilities to solve classical computer problems. The experiments are mostly based on the concept of coordination: subjects have individual incentives that are expected to drive them to cooperate with one another and lead them toward the collective goal ~\cite{nowak:evolutioncooperation}.

@@

The experiments conducted by~\cite{farenzena:collabem} had human beings trying to solve constraint satisfaction problems, namely Boolean Satisfiability (SAT)~\cite{cook:complexitytheoremproving} and the popular \emph{Sudoku} game~\cite{weber:satsudoku}, with individuals connected through the network being able to exchange partial solutions of the problem in question. There were two main patterns of behaviour observed in this study in regard to copying neighbours' solutions:

@@

@@

\subsection{Network Topology}

We modelled our agent networks through the network topologies employed by~\cite{farenzena:collabem} in their tests with human social networks. The topologies used were the {\em fully connected} topology, the {\em scale free} topology~\cite{barabasi:linked}, the {\em ring-2} topology and the {\em ring-3} topology~\cite{newman:newtorks}.

@@

\begin{figure}
\includegraphics[scale=0.45]{progression}
\caption{Progression of the solution. The graph shows how many agents have successfully solved the puzzle in a given iteration (scale-free topology)
}
\label{fig:progression}
\end{figure}

\section{Conclusions and Further Work}

We compared results from social computing experiments done with human subjects with agent-based simulations mimicking the same problem-solving environments. To do this, we proposed a novel method for artificial social problem-solving and used it to model the {\em Sudoku} problem-solving environment studied by~\cite{farenzena:collabem}. We reached important conclusions concerning the dynamics of problem-solving collaborative environments: the behaviours of copying and guessing are shown to be beneficial to these systems. We also discuss the benefits of the behaviour of evaluating neighbours' solutions in order to select one of them for copying, rather than simply selecting a random solution or even the most readily available one, as the analysis conducted by~\cite{farenzena:collabem} has shown to be the case sometimes. With these results in mind, we conjectured that some proprieties of the graphic interface (as ordering the neighbours' solutions by the value of a evaluation function) could guide human subjects into the right direction, improving the performance of the social network. The validation of this hypothesis has been set as our future path and is currently being pursued.
